---
title: ""
format:
  pdf:
    documentclass: article
    papersize: letter
    geometry:
      - margin=1in
      - textwidth=6.5in
    fontsize: 11pt
    linestretch: 1.15
    colorlinks: true
    linkcolor: blue
    urlcolor: blue
header-includes:
  - \usepackage{fancyhdr}
  - \usepackage{lastpage}
  - \usepackage{xcolor}
  - \usepackage{ragged2e}
  - \usepackage{array}
  - \usepackage{enumitem}
  - \usepackage{setspace}
  - \usepackage[T1]{fontenc}
  - \usepackage{mathpazo}
  - \usepackage[explicit]{titlesec}
  - \usepackage{parskip}
  - \usepackage[colorlinks=true,urlcolor=blue]{hyperref}
  - \pagestyle{fancy}
  - \fancyhf{}
  - \renewcommand{\headrulewidth}{0.4pt}
  - \fancyhead[L]{Bryan Acton}
  - \fancyhead[R]{Curriculum Vitae}
  - \fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}
  - \setlength{\parindent}{0pt}
  - \setlength{\parskip}{0.5em}
  - \titleformat{\section}{\Large\bfseries\raggedright}{}{0em}{#1}[\vspace{0.5em}\titlerule]
  - \titlespacing*{\section}{0pt}{1.5em}{1em}
  - \titleformat{\subsection}{\normalsize\bfseries}{}{0em}{#1}
  - \titlespacing*{\subsection}{0pt}{1em}{0.5em}
  - \setlength{\emergencystretch}{3em}
  - \widowpenalty=10000
  - \clubpenalty=10000
  - \raggedbottom
  - \newcommand{\cvitem}[1]{\par\hangindent=2em\hangafter=1\noindent#1\par}
execute:
  echo: false
  warning: false
---

```{r setup, include=FALSE}
library(yaml)
library(knitr)

# Load all data files
personal <- yaml::read_yaml("../data/personal.yaml")
positions <- yaml::read_yaml("../data/positions.yaml")
education <- yaml::read_yaml("../data/education.yaml")
publications <- yaml::read_yaml("../data/publications.yaml")
teaching <- yaml::read_yaml("../data/teaching.yaml")
service <- yaml::read_yaml("../data/service.yaml")
awards <- yaml::read_yaml("../data/awards.yaml")
grants <- yaml::read_yaml("../data/grants.yaml")
media <- yaml::read_yaml("../data/media.yaml")
industry <- yaml::read_yaml("../data/industry.yaml")
presentations <- yaml::read_yaml("../data/presentations.yaml")

# Helper function to escape LaTeX special characters
escape_latex <- function(text) {
  if (is.null(text)) return("")
  text <- gsub("&", " and ", text)
  text <- gsub("_", "\\\\_", text)
  text <- gsub("%", "\\\\%", text)
  text <- gsub("#", "\\\\#", text)
  return(text)
}
```

\begin{center}
{\small Last Updated: `r format(Sys.Date(), "%B %d, %Y")`}

\vspace{1em}
{\LARGE\textbf{`r paste(personal$name$first, personal$name$middle, personal$name$last)`}}

\vspace{1em}
{\normalsize
\begin{tabular}{c}
`r escape_latex(personal$current_position$department)` \\
`r escape_latex(personal$current_position$institution)` \\
\vspace{0.5em}
`r personal$current_position$address$street` \\
Phone: `r personal$contact$phone` \\
Email: `r personal$contact$email` \\
\end{tabular}
}
\end{center}

\vspace{1.5em}
\section*{ACADEMIC POSITIONS}

```{r results='asis'}
if (!is.null(positions$academic_positions)) {
  for (pos in positions$academic_positions) {
    pos_text <- paste0(
      "\\textbf{", escape_latex(pos$title), "}\\\\",
      escape_latex(pos$institution), ", ", escape_latex(pos$department), "\\\\",
      "\\textit{", pos$period, "}"
    )
    if (!is.null(pos$mentor)) {
      pos_text <- paste0(pos_text, "\\\\\n\\textit{Mentor: ", escape_latex(pos$mentor), "}")
    }
    cat("\\cvitem{", pos_text, "}\n\n\\vspace{0.75em}\n", sep="")
  }
}
```

\section*{EDUCATION}

```{r results='asis'}
for (edu in education) {
  cat("\\cvitem{\\textbf{", edu$degree, "}\\hfill", edu$year, "}\n\n", sep="")
  cat("\\cvitem{", escape_latex(edu$institution), "}\n", sep="")
  if (!is.null(edu$department)) {
    cat("\\cvitem{", escape_latex(edu$department), "}\n\n", sep="")
  }
  if (!is.null(edu$advisors)) {
    if (is.character(edu$advisors)) {
      cat("\\cvitem{\\textit{Advisor: ", escape_latex(edu$advisors), "}}\n\n", sep="")
    } else {
      cat("\\cvitem{\\textit{Advisor: ", paste(sapply(edu$advisors, escape_latex), collapse=", "), "}}\n\n", sep="")
    }
  }
  if (!is.null(edu$dissertation)) {
    cat("\\cvitem{\\textit{Dissertation: ", escape_latex(edu$dissertation), "}}\n\n", sep="")
  }
  if (!is.null(edu$honors)) {
    cat("\\cvitem{\\textit{Honors: ", escape_latex(edu$honors), "}}\n\n", sep="")
  }
  cat("\\vspace{1em}\n")
}
```

\section*{PUBLICATIONS}

\subsection*{Journal Articles}

```{r results='asis'}
if (!is.null(publications$peer_reviewed)) {
  for (pub in publications$peer_reviewed) {
    pub_text <- paste0(
      escape_latex(pub$authors), " (", pub$year, "). ",
      escape_latex(pub$title), ". ",
      "\\textit{", escape_latex(pub$journal), "}"
    )
    if (!is.null(pub$pages)) {
      pub_text <- paste0(pub_text, ", ", escape_latex(pub$pages))
    }
    pub_text <- paste0(pub_text, ". ")
    
    # Add DOI with hyperlink
    if (!is.null(pub$doi)) {
      pub_text <- paste0(pub_text, "\\href{https://doi.org/", pub$doi, "}{doi:", pub$doi, "}")
    }
    
    # Add citation count if available
    if (!is.null(pub$citations)) {
      pub_text <- paste0(pub_text, " (Google Scholar citations: ", pub$citations, ")")
    }
    
    cat("\\begin{itemize}\\item ", pub_text, "\\end{itemize}\n\n", sep="")
  }
}
```

\subsection*{Book Chapters}

```{r results='asis'}
if (!is.null(publications$book_chapters)) {
  for (chapter in publications$book_chapters) {
    chapter_text <- paste0(
      escape_latex(chapter$authors), " (", chapter$year, "). ",
      escape_latex(chapter$title), ". In ",
      "\\textit{", escape_latex(chapter$book), "}"
    )
    if (!is.null(chapter$pages)) {
      chapter_text <- paste0(chapter_text, " (pp. ", escape_latex(chapter$pages), ")")
    }
    chapter_text <- paste0(chapter_text, ". ", escape_latex(chapter$publisher))
    
    cat("\\begin{itemize}\\item ", chapter_text, ".\\end{itemize}\n\n", sep="")
  }
}
```

\subsection*{Research Grants}

```{r results='asis'}
if (!is.null(grants$grants)) {
  for (grant in grants$grants) {
    grant_text <- paste0(
      escape_latex(grant$investigators), " ", 
      "\\textit{", escape_latex(grant$title), "}. ",
      escape_latex(grant$agency), ". ",
      grant$grant_number,
      " (\\$", formatC(as.numeric(gsub("[^0-9.]", "", grant$amount)), format="f", digits=0, big.mark=","), ") ",
      "(", grant$period, ")."
    )
    cat("\\begin{itemize}\\item ", grant_text, "\\end{itemize}\n\n", sep="")
  }
}
```

\section*{TEACHING EXPERIENCE}

```{r results='asis'}
if (!is.null(teaching$teaching_experience)) {
  for (exp in teaching$teaching_experience) {
    cat("\\textbf{", escape_latex(exp$institution), "}\n\n", sep="")
    
    for (course in exp$courses) {
      course_text <- paste0(
        "\\textbf{", escape_latex(course$name), "} (", course$level, ")\\\\",
        "Role: ", course$role, "\\\\",
        "Semesters: ", paste(course$semesters, collapse=", "), "\\\\",
        escape_latex(course$description)
      )
      cat("\\cvitem{", course_text, "}\n\n", sep="")
    }
  }
}
```

\section*{TEACHING EVALUATIONS}

```{r results='asis'}
if (!is.null(teaching$teaching_summary$evaluation_summary)) {
  cat("\\textit{", escape_latex(teaching$teaching_summary$evaluation_summary), "}\n\n\\vspace{0.5em}\n\n")
}

if (!is.null(teaching$teaching_experience)) {
  for (exp in teaching$teaching_experience) {
    for (course in exp$courses) {
      if (!is.null(course$evaluations)) {
        cat("\\textbf{", escape_latex(course$name), "}\n\n", sep="")
        
        for (eval in course$evaluations) {
          eval_text <- paste0(
            eval$semester, ":\\\\",
            "Instructor Rating: ", eval$soot_scores$instructor, " (out of 4)\\\\",
            "Course Rating: ", eval$soot_scores$course, " (out of 4)"
          )
          if (!is.null(eval$note)) {
            eval_text <- paste0(eval_text, "\\\\", escape_latex(eval$note))
          }
          cat("\\cvitem{", eval_text, "}\n\n", sep="")
        }
        cat("\\vspace{0.5em}\n\n")
      }
    }
  }
}
```

\section*{CONFERENCE PRESENTATIONS}

```{r results='asis'}
if (!is.null(presentations$conference_presentations)) {
  for (pres in presentations$conference_presentations) {
    pres_text <- paste0(
      escape_latex(pres$authors), " (", pres$year
    )
    if (!is.null(pres$date)) {
      pres_text <- paste0(pres_text, ", ", pres$date)
    }
    pres_text <- paste0(pres_text, "). ", escape_latex(pres$title))
    
    if (!is.null(pres$symposium_info)) {
      pres_text <- paste0(pres_text, ". ", escape_latex(pres$symposium_info))
    }
    
    if (!is.null(pres$type)) {
      pres_text <- paste0(pres_text, " [", escape_latex(pres$type), "]")
    }
    
    pres_text <- paste0(pres_text, ". ", escape_latex(pres$venue))
    
    if (!is.null(pres$location)) {
      pres_text <- paste0(pres_text, ", ", escape_latex(pres$location))
    }
    
    if (!is.null(pres$organizers)) {
      pres_text <- paste0(pres_text, ". (", escape_latex(pres$organizers), ", Organizers)")
    }
    
    cat("\\begin{itemize}\\item ", pres_text, ".\\end{itemize}\n\n", sep="")
  }
}
```

\section*{SERVICE AND LEADERSHIP}

```{r results='asis'}
# Editorial Service
if (!is.null(service$professional_service$editorial)) {
  for (role in service$professional_service$editorial) {
    cat("\\begin{itemize}\\item ", "\\textbf{", escape_latex(role$role), "}", sep="")
    cat("\\\\", escape_latex(role$journal), " (", escape_latex(role$period), ")", sep="")
    if (!is.null(role$details)) {
      cat("\\\\", escape_latex(role$details), sep="")
    }
    cat("\\end{itemize}\n\n")
  }
}

# Virginia Tech Service
if (!is.null(service$institutional_service)) {
  for (inst in service$institutional_service) {
    if (inst$institution == "Virginia Tech") {
      for (role in inst$roles) {
        cat("\\begin{itemize}\\item ", "\\textbf{", escape_latex(role$role), "}", sep="")
        cat("\\\\", escape_latex(role$organization), " (", escape_latex(role$period), ")", sep="")
        if (!is.null(role$description)) {
          cat("\\\\", escape_latex(role$description), sep="")
        }
        cat("\\end{itemize}\n\n")
      }
    }
  }
}

# Binghamton Service
if (!is.null(service$institutional_service)) {
  for (inst in service$institutional_service) {
    if (inst$institution == "Binghamton University") {
      for (role in inst$roles) {
        cat("\\begin{itemize}\\item ", "\\textbf{", escape_latex(role$role), "}", sep="")
        cat("\\\\", escape_latex(inst$institution), " (", escape_latex(role$period), ")", sep="")
        if (!is.null(role$description)) {
          cat("\\\\", escape_latex(role$description), sep="")
        }
        cat("\\end{itemize}\n\n")
      }
    }
  }
}
```

\section*{HONORS AND AWARDS}

```{r results='asis'}
if (!is.null(awards$awards)) {
  for (award in awards$awards) {
    award_text <- paste0(
      "\\textbf{", escape_latex(award$title), "}"
    )
    if (!is.null(award$organization)) {
      award_text <- paste0(award_text, "\\\\", escape_latex(award$organization))
    }
    if (!is.null(award$year)) {
      award_text <- paste0(award_text, " (", award$year, ")")
    }
    if (!is.null(award$description)) {
      award_text <- paste0(award_text, "\\\\", escape_latex(award$description))
    }
    cat("\\begin{itemize}\\item ", award_text, "\\end{itemize}\n\n", sep="")
  }
}
```

\section*{MEDIA AND PRESS}

```{r results='asis'}
if (!is.null(media$media_appearances)) {
  for (item in media$media_appearances) {
    media_text <- paste0(
      "\\textbf{", escape_latex(item$title), "}\\\\",
      escape_latex(item$type), " - ", escape_latex(item$outlet)
    )
    if (!is.null(item$date)) {
      media_text <- paste0(media_text, " (", item$date, ")")
    }
    if (!is.null(item$description)) {
      media_text <- paste0(media_text, "\\\\", escape_latex(item$description))
    }
    if (!is.null(item$url)) {
      media_text <- paste0(media_text, "\\\\\\url{", item$url, "}")
    }
    if (!is.null(item$details)) {
      media_text <- paste0(media_text, "\\\\", escape_latex(item$details))
    }
    cat("\\begin{itemize}\\item ", media_text, "\\end{itemize}\n\n", sep="")
  }
}
```

\section*{INDUSTRY EXPERIENCE}

```{r results='asis'}
if (!is.null(industry$industry_experience)) {
  for (exp in industry$industry_experience) {
    industry_text <- paste0(
      "\\textbf{", escape_latex(exp$role), "}\\\\",
      escape_latex(exp$organization)
    )
    if (!is.null(exp$period)) {
      industry_text <- paste0(industry_text, " (", exp$period, ")")
    }
    if (!is.null(exp$responsibilities)) {
      industry_text <- paste0(industry_text, "\\\\", paste(sapply(exp$responsibilities, escape_latex), collapse="\\\\"))
    }
    if (!is.null(exp$impact)) {
      industry_text <- paste0(industry_text, "\\\\", escape_latex(exp$impact))
    }
    cat("\\begin{itemize}\\item ", industry_text, "\\end{itemize}\n\n", sep="")
  }
}
```

\section*{PROFESSIONAL PRESENTATIONS \& WORKSHOPS}

```{r results='asis'}
if (!is.null(presentations$professional_presentations)) {
  for (pres in presentations$professional_presentations) {
    pres_text <- paste0(
      "\\textbf{", escape_latex(pres$title), "}\\\\",
      escape_latex(pres$venue)
    )
    if (!is.null(pres$date)) {
      pres_text <- paste0(pres_text, " (", pres$date, ")")
    }
    if (!is.null(pres$description)) {
      pres_text <- paste0(pres_text, "\\\\", escape_latex(pres$description))
    }
    cat("\\begin{itemize}\\item ", pres_text, "\\end{itemize}\n\n", sep="")
  }
}
```